Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-13 Supplementary_figures.tex
finallized
Updates from Overleaf
new Table 1 (merged table 1 and table 2)

@@

\begin{document}
%%%%%%%%% title
% Full title of the paper (Capitalized)
%\Title{
Title: A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma\\[2cm]
%}

@@

\underline{Supplementary figure legends}\\[1cm]
% S1
Supplementary Figure \ref{fig:fig_SurvExpress}\\
The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of high risk and low risk groups, which is derived from risk groups optimization. %cumulative P-value plots).
Inset color scale shows risk groups (high/low) and corresponded RNA expression in high/low.
Thus, the poor prognostic genes are marked as red; the better prognostic genes are marked as orange.

%S2
Supplementary Figure \ref{fig:fig_HPA_USP10}\\
The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
Over-expression of USP10 has poor prognosis on HNSCC.

%S3
Supplementary Figure \ref{fig:fig_GSE2837}\\
GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as red; the better prognostic genes are marked as green.

% SFigure 1, SurvExpress

% red or green is NOT by expression level
\begin{figure}
\raggedleft
\includegraphics[width=10cm]{Answer_3-1.pdf}
\caption{The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{green}{low risk} groups, which is derived from risk groups optimization. %cumulative P-value plots).
Inset color scale shows risk groups (\textcolor{red}{high}/\textcolor{green}{low}) and corresponded RNA expression in \textcolor{red}{high}/\textcolor{green}{low}.
Thus, the poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{orange}{orange}.}
\label{fig:fig_SurvExpress}
\end{figure}
%\clearpage

@@

\begin{figure}
\raggedleft
\includegraphics[width=12cm]{Answer_3-1_USP10.pdf}
\caption{The query results from HPA: Kaplan-Meier plots of  ubiquitin specific peptidase 10 (USP10) with cutoff by mRNA \textcolor{red}{high expression} and \textcolor{blue}{low expression} groups (P-value = 0.0018).
Overexpression of USP10 has poor prognosis on HNSCC.}
\label{fig:fig_HPA_USP10}
\end{figure}
%\clearpage

% from Answer2-2 GSE2837

\begin{figure}
\raggedleft
\includegraphics[width=12cm]{Answer_2-2.pdf}
\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
\label{fig:fig_GSE2837}
\end{figure}
%\clearpage

>>>>

% \usepackage{multirow}
\usepackage{graphicx}
\usepackage[table,xcdraw]{xcolor}

\usepackage{siunitx} % for  1e-10 scientific notation
\usepackage{array}
\usepackage{ragged2e}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{makecell}
% \usepackage{array}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{hhline}

@@

\begin{document}
%%%%%%%%% title
% Full title of the paper (Capitalized)
%\Title{
x Title: A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma\\[2cm]
%}

@@

\section{STables}
\underline{Supplementary figure legends}\\[1cm]
%ST1
Supplementary Table \ref{table:table1}\\
GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as red; the better prognostic genes are marked as green.

%ST2
Supplementary Table \ref{table:table3}\\

% tables below %%%%
% table1
\begin{table}
%\begin{sidewaystable}[hp]
\centering
\caption{ The top 10 genes overexpressed with poor prognosis in \acrshort{hnscc} (ranked by adjusted \textit{P} value) }
\arrayrulecolor[rgb]{0.255,0.255,0.255}
\resizebox{\linewidth}{!}{
%\begin{tabular}{|l|l|l|l|l|l|l|l|c|}
\begin{tabularx}{\textwidth}{|l|p{3.5cm}|l|l|l|l|l|l|c|} % *** capital X or p{2cm}
% p{2cm}
\hline
\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}}     & \multicolumn{2}{c|}{Kaplan-Meier survival}                                                                                   & \multicolumn{2}{c|}{Univariate~}                                                        & \multicolumn{2}{c|}{Multivariate}                                                       & \multirow{2}{*}{Remark}                     \\ 
\cline{3-8}
\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                      & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}FDR \\\textit{P} value\end{tabular}}               & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Bonferroni \\\textit{P} value\end{tabular}} & \multicolumn{1}{c|}{HR*}                   & 95\% CI                                    & HR*                                        & 95\% CI                                    &                                             \\ 
\hline
DKK1                                           & dickkopf WNT signaling pathway inhibitor 1                 & \num{8.9e-8}                               & 0.001                                                                           & 2.266                                      & 1.666-3.082                                & 2.135                                      & 1.559-2.924                                &                                           \\ 
\hline
CAMK2N1                                        & calcium/calmodulin-dependent protein kinase II inhibitor 1 & \num{2.9e-7}                               & 0.002                                                                           & 2.101                                      & 1.572-2.809                                & 2.007                                      & 1.490-2.704                                & \checkmark                                          \\ 
\hline
STC2                                           & stanniocalcin 2                                            & \num{6.5e-7}                               & 0.004                                                                           & 2.147                                      & 1.578-2.921                                & 2.075                                      & 1.515-2.843                                &                                           \\ 
\hline
PGK1                                           & phosphoglycerate kinase 1                                  & \num{9.1e-7}                               & 0.006                                                                           & 2.127                                      & 1.563-2.895                                & 2.046                                      & 1.498-2.795                                & \checkmark                                          \\ 
\hline
SURF4                                          & surfeit 4                                                  & \num{9.6e-7}                               & 0.006                                                                           & 2.055                                      & 1.531-2.757                                & 2.089                                      & 1.543-2.829                                & \checkmark                                           \\ 
\hline
USP10                                          & ubiquitin specific peptidase 10                            & \num{1.7e-6}                               & 0.012                                                                           & 2.083                                      & 1.532-2.834                                & 2.119                                      & 1.551-2.895                                & \checkmark                                         \\ 
\hline
NDFIP1                                         & Nedd4 family interacting protein 1                         & \num{2.6e-6}                               & 0.017                                                                           & 2.031                                      & 1.502-2.746                                & 2.027                                      & 1.483-2.771                                & \checkmark                                           \\ 
\hline
FOXA2                                          & forkhead box A2                                            & \num{2.7e-6}                               & 0.018                                                                           & 1.976                                      & 1.479-2.640                                & 1.914                                      & 1.426-2.569                                & \checkmark                                          \\ 
\hline
STIP1                                          & stress-induced-phosphoprotein 1                            & \num{4.3e-6}                              & 0.029                                                                           & 1.958                                      & 1.463-2.621                                & 1.957                                      & 1.451-2.640                                &                                           \\ 
\hline
DKC1                                           & dyskeratosis congenita 1, dyskerin                         & \num{6.3e-6}                               & 0.042                                                                           & 2.046                                      & 1.490-2.808                                & 1.837                                      & 1.332-2.534                                &                                           \\ 
\hline
\multicolumn{1}{|l!{\color{black}\vrule}}{}    & \multicolumn{1}{l!{\color{black}\vrule}}{}                 & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}                                      & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{} & \multicolumn{1}{l!{\color{black}\vrule}}{}  \\ 
\arrayrulecolor{black}\hline
\multicolumn{9}{|l!{\color{black}\vrule}}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} $< 0.05 $~\\~Cox's univariate and multivariate$ HR >= 1.5$ \end{tabular}}                                                                                                                                                                                                                                                              \\ 
\hline
\multicolumn{9}{|l!{\color{black}\vrule}}{* Cox's model: \textit{P} $< 0.001$ }                                                                                                                                                                                                                                                                                                                                                                                                  \\ 
\hline
\multicolumn{9}{|l!{\color{black}\vrule}}{Remark: \checkmark validated by GSE2837}                                                                                                                                                                                                                                                                                                                                                             \\
\hline
\end{tabularx}
}
\arrayrulecolor{black}
\label{table:table1}

%\end{sidewaystable}
\end{table}

%%%
%Table2. The 10 candidate genes overexpressed with better prognosis in HNSCC (ranked by Bonferroni corrected Kaplan-Meier P-value).
\begin{table}[hp]
\centering
\caption{The other top 10 genes overexpressed with better prognosis in \acrshort{hnscc} (ranked by corrected \textit{P} value) }
\arrayrulecolor[rgb]{0.255,0.255,0.255}
\resizebox{\linewidth}{!}{%
\begin{tabular}{|l|l|l|l|l|l|l|l|c|} 
\hline
\multicolumn{1}{|c|}{\multirow{2}{*}{Gene ID}} & \multicolumn{1}{c|}{\multirow{2}{*}{Gene Description}} & \multicolumn{2}{l|}{Kaplan-Meier survival}                                                                                                                                                & \multicolumn{2}{c|}{Univariate~}                                                                        & \multicolumn{2}{c|}{Multivariate}                                                                       & \multicolumn{1}{l|}{\multirow{2}{*}{Remark}}  \\ 
\cline{3-8}
\multicolumn{1}{|c|}{}                         & \multicolumn{1}{c|}{}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}FDR\\~\textit{P} value\end{tabular}}                                  & \multicolumn{1}{c!{\color{black}\vrule}}{\begin{tabular}[c]{@{}c@{}}Bonferroni\\~\textit{P} value\end{tabular}} & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{c!{\color{black}\vrule}}{HR*}   & \multicolumn{1}{c!{\color{black}\vrule}}{95\% CI}     & \multicolumn{1}{l|}{}                         \\ 
\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
ZNF557                                         & zinc finger protein 557                                & \multicolumn{1}{l!{\color{black}\vrule}}{\textcolor[rgb]{0,0,0.471}{\num{8.6e-8}}} & \multicolumn{1}{l!{\color{black}\vrule}}{0.001}                                                      & \multicolumn{1}{l!{\color{black}\vrule}}{0.465} & \multicolumn{1}{l!{\color{black}\vrule}}{0.348-0.619} & \multicolumn{1}{l!{\color{black}\vrule}}{0.499} & \multicolumn{1}{l!{\color{black}\vrule}}{0.372-0.669} &                                              \\ 
\cline{1-2}\arrayrulecolor{black}\cline{3-8}\arrayrulecolor[rgb]{0.255,0.255,0.255}\cline{9-9}
ZNF266                                         & zinc finger protein 266                                & \textcolor[rgb]{0,0,0.471}{\num{2.2e-7}}                                           & 0.001                                                                                                & 0.474                                           & 0.355-0.632                                           & 0.453                                           & 0.338-0.607                                           &                                              \\ 
\hline
IL19                                           & interleukin 19                                         & \textcolor[rgb]{0,0,0.471}{}\num{3.7e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.002                                                                                                & 0.472                                           & 0.351-0.635                                           & 0.459                                           & 0.340-0.619                                           & \checkmark                                            \\ 
\hline
MYO1H                                          & myosin 1H                                              & \textcolor[rgb]{0,0,0.471}{}\num{3.8e-7}\textcolor[rgb]{0,0,0.471}{}               & 0.003                                                                                                & 0.468                                           & 0.347-0.632                                           & 0.467                                           & 0.344-0.634                                           &                                              \\ 
\hline
FCGBP                                          & Fc fragment of IgG binding protein                     & \textcolor[rgb]{0,0,0.471}{}\num{1.2e-6}\textcolor[rgb]{0,0,0.471}{}               & 0.008                                                                                                & 0.484                                           & 0.359-0.653                                           & 0.496                                           & 0.366-0.674                                           &  \checkmark                                           \\ 
\hline
LOC148709                                      & LncRNA LOC148709                                       & \textcolor[rgb]{0,0,0.471}{\num{1.5e-6}}                                           & 0.010                                                                                                & 0.499                                           & 0.374-0.666                                           & 0.485                                           & 0.361-0.652                                           &                                              \\ 
\hline
EVPLL                                          & envoplakin-like protein                                & \textcolor[rgb]{0,0,0.471}{\num{2.0e-6}}                                           & 0.013                                                                                                & 0.490                                           & 0.363-0.661                                           & 0.494                                           & 0.364-0.672                                           &                                              \\ 
\hline
PNMA5                                          & paraneoplastic antigen like 5                          & \textcolor[rgb]{0,0,0.471}{\num{2.6e-6}}                                           & 0.017                                                                                                & 0.499                                           & 0.371-0.671                                           & 0.481                                           & 0.357-0.650                                           &                                              \\ 
\hline
KIAA1683                                       & new name as IQ Motif Containing N (IQCN)                           & \textcolor[rgb]{0,0,0.471}{\num{3.1e-6}}                                           & 0.020                                                                                                & 0.500                                           & 0.371-0.673                                           & 0.483                                           & 0.356-0.654                                           &   \checkmark                                           \\ 
\hline
NPB                                            & neuropeptide B                                         & \textcolor[rgb]{0,0,0.471}{\num{4.0e-6}}                                           & 0.027                                                                                                & 0.460                                           & 0.328-0.646                                           & 0.457                                           & 0.324-0.646                                           &      \checkmark                                        \\ 
\hline
                                               &                                                        &                                                                                    &                                                                                                      &                                                 &                                                       &                                                 &                                                       & \multicolumn{1}{l|}{}                         \\ 
\hline
\multicolumn{9}{|l|}{\begin{tabular}[c]{@{}l@{}}Selection criteria:~\\~Kaplan-Meier Bonferroni-adjusted \textit{P} value \textless{} 0.05~\\~Cox's univariate and multivariate HR \textgreater{}= 1.5\\
%\hline
%\multicolumn{9}{|l!{\color{black}\vrule}}{
* Cox's model: \textit{P} $< 0.001$ \\
%}                                                                                                                                                                                                                                                                                                                                                                                                  \\ 
%\hline
lncRNA: Long non-coding RNA\\Remark: \checkmark Validated by GSE2837 ~\end{tabular}}                                                                                                                                                                                                                 \\
\hline
\end{tabular}
}
\arrayrulecolor{black}
\label{table:table3}
\end{table}

@@

\section{SFigures}
\underline{Supplementary figure legends}\\[1cm]
%S1
Supplementary Figure \ref{fig:fig_GSE2837}\\
GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as red; the better prognostic genes are marked as green.

% x S2
Supplementary Figure \ref{fig:fig_SurvExpress}\\
The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of high risk and low risk groups, which is derived from risk groups optimization. %cumulative P-value plots).
Inset color scale shows risk groups (high/low) and corresponded RNA expression in high/low.
Thus, the poor prognostic genes are marked as red; the better prognostic genes are marked as orange.

%x S3
Supplementary Figure \ref{fig:fig_HPA_USP10}\\
The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
Over-expression of USP10 has poor prognosis on HNSCC.

%%%%%
% S1
% from Answer2-2 GSE2837; 
\begin{figure}
\raggedleft
\includegraphics[width=12cm]{Answer_2-2.pdf}
\caption{GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{blue}{low risk} groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{green}{green}.}
\label{fig:fig_GSE2837}
\end{figure}

% SFigure 2, SurvExpress
% red or green is NOT by expression level
\begin{figure}
\raggedleft
\includegraphics[width=10cm]{Answer_3-1.pdf}
\caption{The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of \textcolor{red}{high risk} and \textcolor{green}{low risk} groups, which is derived from risk groups optimization. %cumulative P-value plots).
Inset color scale shows risk groups (\textcolor{red}{high}/\textcolor{green}{low}) and corresponded RNA expression in \textcolor{red}{high}/\textcolor{green}{low}.
Thus, the poor prognostic genes are marked as \textcolor{red}{red}; the better prognostic genes are marked as \textcolor{orange}{orange}.}
\label{fig:fig_SurvExpress}
\end{figure}
\clearpage

%%
% S3
\begin{figure}
\raggedleft
\includegraphics[width=12cm]{Answer_3-1_USP10.pdf}
\caption{The query results from HPA: Kaplan-Meier plots of  ubiquitin specific peptidase 10 (USP10) with cutoff by mRNA \textcolor{red}{high expression} and \textcolor{blue}{low expression} groups (P-value = 0.0018).
Overexpression of USP10 has poor prognosis on HNSCC.}
\label{fig:fig_HPA_USP10}
\end{figure}
%\clearpage

%\clearpage
